T-reX: Quantifying waste and material footprints in current and future Life Cycle Assessment (LCA) databases

### 2025-02-16 03_T-reX-latex_files-atfirstsubmission/latex_files-atfirstsubmission/cover_letter.tex
auto-update

We are pleased to submit our original research article titled ``T-reX\: A Python Package to Quantify Supply Chain Flows of Waste and Material in LCA Databases'' for consideration by \textit{Resources, Conservation and Recycling}. This manuscript details the development and application of an innovative tool designed to improve the quantification of waste and material flows within Life Cycle Assessment (LCA) databases, an essential aspect of progressing towards sustainable resource management and circular economy objectives.

Our submission provides a comprehensive description of the tool, which integrates seamlessly with the Brightway2 framework to offer a user-friendly and adaptable solution for LCA practitioners. By automating data analysis and aggregation processes, our tool expedites the identification of environmental hotspots within supply chains, thus facilitating more informed decision-making.

>>>>

    We are pleased to submit our original research article titled ``T-reX: Quantifying waste and material footprints in current and future Life Cycle Assessment (LCA) databases'' for consideration by \textit{Resources, Conservation and Recycling}. This manuscript details the development and application of an innovative tool designed to improve the quantification of waste and material flows within Life Cycle Assessment (LCA) databases, an essential aspect of progressing towards sustainable resource management and circular economy objectives.

    Our submission provides a comprehensive description of the tool, which integrates seamlessly with the \texttt{brightway} framework to offer a user-friendly and adaptable solution for LCA practitioners. By automating data analysis and aggregation processes, our tool expedites the identification of environmental hotspots within supply chains, thus facilitating more informed decision-making.
